A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
cox & -- & 0.847 & -- & 0.238 & 0.162 \\
log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & -1159.72 & 0.79 & -1159.72 & 0.21 & 0.13 \\
Cox & -- & 0.79 & -- & 0.13 & 0.07 \\
Log Logistic & -1313.15 & 0.78 & -1313.15 & 0.20 & 0.12 \\
Log Normal & -1299.38 & 0.79 & -1299.38 & 0.20 & 0.12 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
cox & -- & 0.888 & -- & 0.185 & 0.201 \\
log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & -1631.26 & 0.90 & -1631.26 & 0.15 & 0.09 \\
Cox & -- & 0.90 & -- & 0.11 & 0.05 \\
Log Logistic & -1842.71 & 0.90 & -1842.71 & 0.14 & 0.08 \\
Log Normal & -1799.93 & 0.90 & -1799.93 & 0.14 & 0.08 \\
\bottomrule
\end{tabular}
\end{table*}
